\documentclass{grattanAlpha}

\begin{document}

Take heed that ye do not your alms before men, to be seen of them: otherwise ye have no reward of your Father which is in heaven. Therefore when thou doest thine alms, do not sound a trumpet before thee, as the hypocrites do in the synagogues and in the streets, that they may have glory of men. Verily~I say unto you, They have their reward.  But when thou doest alms, let not thy left hand know what thy right hand doeth: that thine alms may be in secret: and thy Father which seeth in secret himself~shall reward thee~openly.

And God said, “Let there be lights in the vault of the sky to separate the day from the night, and let them serve as signs to mark sacred times, and days and years, and let them be lights in the vault of the sky to give light on the earth.” And it was so. God made two great lights—the greater light to govern the day and the lesser light to govern the night. He also made the stars. God set them in the vault of the sky to give light on the earth, to govern the day and the night, and to separate light from darkness. And God saw that it was good. And there was evening, and there was morning—the fourth day.

And God said, “Let the water teem with living creatures, and let birds fly above the earth across the vault of the sky.” So God created the great creatures of the sea and every living thing with which the water teems and that moves about in it, according to their kinds, and every winged bird according to its kind. And God saw that it was good. God blessed them and said, “Be fruitful and increase in number and fill the water in the seas, and let the birds increase on the earth.” And there was evening, and there was morning—the fifth day.
\end{document}
